Resilience and Home-Space for WSTS

### 2024-01-05 diapo/presentation.tex
up

@@

>>>>

 \begin{theorem}[Theorem 1,~\cite{DBLP:conf/gg/Ozkan22}, Theorem 1, ~\cite{DBLP:journals/corr/abs-2108-00889}]\label{ref ozkan}
{\sc Bounded-state-resilience} and {\sc $k$-state-resilience} are decidable for $\pred$-basis-effective, $\post^*$-basis-effective WSTS with strong compatibility
when
$\Safe=\mathop{\uparrow} \Safe$.
\end{theorem}

% Keeping the $\mathop{\uparrow} \post^*$ effectiveness hypothesis but \emph{loosening} the strong compatibility one still yields some decidability result for the general {\sc State-resilience}. Using the same proof structure as Theorem 1 from \cite{DBLP:journals/corr/abs-2108-00889} we obtain:

\begin{theorem}\label{post srp}
{\sc State-resilience} is decidable for $\pred$-basis-effective, $\post^*$-basis-effective WSTS
when
$\Safe=\mathop{\uparrow} \Safe$. 
\end{theorem}

@@

- Resilience $\to$ inclusion d'idéaux

- Bounded resilience and $k$-resilience $\to$ more complex

- Remaque sur les VAS : it does not hold

- Remarque additionnelle du coup

-
